Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-16 paper/main.tex
alls per call site per run: table and histogram

>>>>

\begin{figure}[h]
    \centering
    \begin{tabular}{|r@{\,}r@{\,}lr|r@{\,}r@{\,}lr|} \hline
        \tt 0 &--& \tt 50      & \Runbina  & \tt 501 &--&\tt 1000  & \Runbine\\
        \tt 51 &--& \tt 100    & \Runbinb  & \tt 1001 &--&\tt 1500  & \Runbinf\\
        \tt 101 &--& \tt 250    & \Runbinc  & \tt 1501 &--&\tt 2000   & \Runbing\\
        \tt 251 &--& \tt 500    & \Runbind  & \tt 2001 &--& \tt 3000 & \Runbinh\\\hline
    \end{tabular}
    \caption{Invocations of \eval per call sites normalized by the number of runs.} \label{tab:callsitesnormalized}
\end{figure}

Figure~\ref{tab:callsitesnormalized} shows the number of invocation to \eval and its variants per call sites per run exercising that call site. If that number is high, it can correspond to a function with an \eval call site that is used widely.   If that number is very high, more than 1000, we expect it to correspond to an \eval call site in a loop. Most of the invocations are less than 50 per run per call site. When zooming in, on Figure~\ref{fig:callsitesnormalized}, most call sites have actually only one invocation per run.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{calls_per_run_per_call_site}
    \caption{Invocations of \eval per call sites normalized by the number of runs, for less than 50 normalized invocations. Binsize is 1} \label{fig:callsitesnormalized}
\end{figure}
